Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-08-28 snapshot_system/fast14_deduplication.tex
change to usenix format

\section{VM-centric Snapshot Deduplication}
\label{sect:dedupe}
%snapshot representation

%We use the The deduplication process is first conducted among snapshots within each VM
%and then is conducted across VMs.
%Given the concern that searching duplicates across VMs is a global feature which can affect parallel performance
%and complicate failure management,
%we only eliminate the duplication of a small but popular data set while still maintaining a cost-effective deduplication ratio.
%For this purpose, we exploit the data characteristics of snapshots and collect most popular data.
%Data sharing across VMs is limited within this small data set such that adding replicas for it could enhance fault tolerance

%A deduplication scheme compares the fingerprints of the current snapshot
%with its parent snapshot and also other snapshots in the entire cloud.
%The traditional approach compares all fingerprints and 
%stores one copy for all of a chunk's duplicates.
%We call this as  the VM-oblivious (VO) approach.

%Our VC design has the following  objectives: 1)  localizing deduplication while identifying a decent amount of
%duplicates among VMs to maintain a competitive deduplication efficiency and simplify snapshot management;
%2) Minimizing the number of file system blocks shared among VMs and adding extra replicas for shared blocks.

\comments{
\begin{itemize}
\item
1) Localize the deduplication and data blocking within each VM as much as possible so 
that any failure of a file system block mainly affects the associated VM.
Localizing the snapshot data deduplication within a VM
improves the system by increasing data independence between different VM backups,
simplifying snapshot management and statistics collection,
and facilitating parallel execution of snapshot operations.
\item
2) Maintain a competitive deduplication efficiency while being resource-friendly to other
existing cloud services.
Cross-VM duplication can be desirable since  there are many cloud images
use widely-used software and libraries and their data blocks are duplicate. 
As the result, different VMs tend to backup large amount of highly similar data.
\item
\end{itemize}
}
\subsection{Key VM-centric  Strategies}
\label{sect:vc-strategies}

%Inner-VM duplication can be very effective within VM's snapshots. There
%are typically a large number of duplicates existing among the snapshots
%for a single VM.

%Our multi-level pipeline process can minimize 
%the cost of deduplication while maximize the its efficiency at each level,
%and it is parallel since each segment is processed independently.

%Our VC differentiates duplicates within a VM and cross VMs,
%and conducts \textit{Inner-VM} and \textit{cross-VM} detection separately.

\begin{itemize}
\item \textbf{VM-specific local duplicate search within similar segments.}
We start with the standard dirty bit approach in a coarse grain segment level.
In our implementation with Xen at an Alibaba platform, the segment size is 2MB
and  the device driver is extended to support  changed block tracking. 
Since every write for a segment will touch a dirty bit, the device driver maintains dirty bits in memory
and cannot afford a small segment  size.
%Xen doesn't directly support it, However, their open-source 
%architecture allows anyone to extend 
%and use the  Xen virtual device driver to implement a feature called ``changed block tracking''
%for the storage device and the dirty bit setting is maintained in a coarse grain level we call it a segment.
It should be noted that dirtybit tracking is supported or can be easily implemented in 
major virtualization solution vendors. For example,
%(VMware, Xen, Microsoft).  
%VMware support it directly; 
the VMWare hypervisor has an API to let external backup applications know 
the changed areas since last backup. 
%We implement dirty bit tracking this way in Alibaba's platform.  
The Microsoft SDK provides an API that allows external applications to monitor 
the VM's I/O traffic and implement  the changed block tracking feature.

Since the best deduplication uses a nonuniform chunk size 
in the average of 4K or 8K~\cite{??},  
%This allows the system to achieve deduplication even when there are insertions/deletions which would
%affect many fixed-size chunks.
we conduct additional local inner-VM deduplication by comparing
dirty segment's chunk fingerprints within  {\em similar} segments from its parent snapshot. 
We define two segments are similar if their approximated content signature is the same.
This segment signature value is defined as the minimum value of all its chunk fingerprints 
computed during backup and is recorded in the snapshot recipe.
When we are processing a dirty segment,
we can easily find similar segments from the
parent snapshot recipe and load their segment recipes and also set a limit on the 
the number of  similar segments to be  searched. 
 Then 
given a set of data chunks within a dirty segment,  we compare  these chunk fingerprints
with those in similar segments.  
For example, with a 2MB segment, there are about 500 fingerprints to compare. By limiting at most 10 similar
segments to search,
the amount of memory for maintaining those fingerprints in similar segment s is small.
% as we only load one dirty segment at a time.

%If we use 4KB in level-1, then such a level-1 should have similar dedup efficiency 
%as the current level-1 and level-2 combined, because finally they equal to comparing  
%parent snapshot at 4KB granularity.
%
%However, at level-3 things are different. If we use 4KB fix-size block uniformly, it would be harder for different VM to share data through PDS, because there is no guarantee that the location of duplicate data on different VM disks are always aligned at 4KB boundary. For example, if two VMs each has a copy of duplicate data, but they are not aligned, then we won't be able to detect them. Our study at the current small data set has shown that using 4KB fix-size block will make PDS method less efficient by nearly 10%. Over the long time, more and more OS variations will co-exist in the cluster, making this 4KB fix-size approach inefficient in reducing duplicate data across VMs.

%\item \textit{Level 2  Chunk fingerprint comparison.}
%If a segment is modified, we perform fine-grained deduplication 
%by comparing the fingerprints of its chunks to the same segment's recipe in the previous snapshot,
%thus eliminate partial data duplication within the segment.
%\end{itemize}
%
%In general, operations at level 1 have almost no cost and most of unmodified data are filtered here. 
%To process a dirty segment at level 2, 
%there requires no more than one DFS access to load the segment recipe from previous snapshot,
%and a tiny amount of memory to hold it in main memory.

\item \textbf{Cross-VM deduplication with popular chunks and replication support}
This step accomplishes the standard global fingerprint  comparison as conducted
in the previous work~\cite{??}.
One key observation is that the inner deduplication has removed many of the duplicates.
There are fewer deduplication opportunities across VMs while the memory and network
consumption for global comparison is more expensive.
Thus our approximation is that the global fingerprint comparison only searches for the top $k$
most popular items. This dataset is called PDS (common data set). 
%Since duplicate sharing patterns among  VM follows a zip-like distribution,  
The popularity of a chunk is the number  of data chunks  from different VMs
that are duplicates of this chunk after the inner VM deduplication.
This number can be computed periodically on a weekly basis.
Once the popularity of all data chunks is collected, the system only maintains the top $k$
most popular chunk signatures in a distributed shared memory.  
%For cross-VM comparison, we only store  top $k$ items and $k$ is chosen to be relatively small.

Since $k$ is relatively small and these top $k$ chunks are shared among multiple VMs, 
we can afford to provide extra replicas for these popular chunks to enhance the fault resilience.
%We will provide an analysis of the space need and fault tolerance in the next subsection.

@@

We have not  adopted the  sampled index~\cite{Guo2011} 
for  popular data chunks and  this is because sampling requires the use of prefetching to be effective.
%For a small set of popular data chunks, the prefetching strategy
%used In the sampled index will not work well because 
For the data sets we have tested, the spatial locality is limited among popular
data chunks and  on average the number of consecutive data chunks is 7 among popular chinks, which is not sufficient.
%to be effective for index sampling.

 \subsection{Impact on deduplication efficiency}
%VM-oriented Fault Isolation}
%Our objective for fault isolation is to minimize the number of VMs affected when there are failures
%in the cluster.  
%The inner-VM deduplication does not depend on any global service and the comparison
%for each VM is localized within the parent and the current snapshot.
%Lack of data dependence between VMs brings 
%Our analysis below will show that the algorithm can still deliver competitive
%deduplication efficiency after making these approximations.
%With cross-VM deduplication, shared data chunks
%create an artificial dependence  among VMs. 
%Thus we only maintain the index for the most popular chunks to reduce the inter-VM dependence
%while still accomplishing competitive deduplication efficiency.

%The management for popular data chunks contains two aspects.

Choosing the value  $k$ for the most popular chunks affects the deduplication efficiency.
%It also  compares the  fault resilience of our VM-centric deduplication approach with a standand approach using 
%global deduplication.
%\subsubsection{Impact of PDS deduplication}
We analyze this impact based on the characteristics  of the VM snapshot traces
studied from  application datasets.
Our previous study shows that the popularity of data chunks after inner VM deduplication follows 
a Zipf-like distribution\cite{zipf} and its
exponent $\alpha$ is ranged between 0.65  and  0.7.~\cite{ieeecloud}. 
%As a result, it can be proved that deduplication efficiency of PDS index is scalable:
Table~\ref{tab:symbol} lists parameters used in this analysis.

@@

%We define deduplication efficiency $e$ to be the proportion of raw data that can be deduplicated,
%In complete deduplication scenario, it deduplication efficiency $e_c$ is:
%\begin{equation}
%e_c = \frac{b-b_u}{b} = 1 - \frac{b_u}{b}
%\end{equation}

@@

%\begin{equation}
%\begin{split}
%e_k &= (\sum_{i=1}^{k}C_i - k)/{b} = (b * \frac{1-\alpha}{b_u^{1-\alpha}} * \sum_{i=1}^{k}\frac{1}{i^\alpha} - k)/b \\
%&\approx \frac{b*\frac{1-\alpha}{b_u^{1-\alpha}}*\frac{k^{1-alpha}}{1-\alpha} - k}{b}
%&\approx (\frac{k}{b_u})^{1-\alpha} - \frac{k}{b} \approx (\frac{k}{b_u})^{1-\alpha},\; (since\; k \ll b)
%\end{split}
%\end{equation}

% For the Zipf-like distribution, an approximation to the sum of the first $n$ 
% elements of the distribution can be derived as follows:
% \begin{equation}
% \sum_{i=1}^{n}\frac{1}{i^\alpha}\approx \int_{1}^{n}\frac{1}{x^\alpha}\mathrm{d}x=\frac{x^{1-\alpha}}{1-\alpha}=\frac{n^{1-\alpha}}{1-\alpha}\;  for\;  \alpha<1
% \end{equation}

% So the cumulative distribution function for a PDS holding top $S_c$ fingerprints
% of global index with size $S_g$ is:

% \begin{equation}
%   E = (S_c / S_g)^{1-\alpha} \;  for\;  \alpha<1
% \end{equation}

%[Describe the dedup efficiency model in detail]
%Let $p$ be the number of physical machines in the cluster, $m$ be the memory on each node used by the popular
%index, $E$ be the size of an index entry,
%$D$ be the amount of unique data on each physical machine, and 
%$C$ be the average chunks size. 
%Then $k$ and $c_u$ can be expressed as:
%$ k = p*m/E$, and $c_u = p*D/E.  $
We store the popular index using a distributed shared memory hashtable such as MemCacheD
and allocate a fixed percentage of memory space   per physical machine for top $k$ popular items.
As the number of physical machines ($p$) increases,
the entire cloud cluster can host more VMs; however,  ratio $\sigma$ which is $k/c_u$ remains
a constant because each physical machine on average still hosts a fixed constant number of 
VMs. Then the overall deduplication efficiency of VC defined in Formula~\ref{eq:dedupeff}
remains to be a constant.
Thus the deduplication efficiency is stable  as $p$ increases as long as $\sigma$  is a constant.

%where $(\frac{m*C}{D*E})^{1-\alpha}$ represents 
Ratio $\sigma^{1-\alpha}$ represents the percentage of the remaining
chunks detected as duplicates in global cross-VM deduplication due to PDS.
We call it PDS coverage.
Figure~\ref{fig:cds-coverage} shows predicted PDS coverage using $\sigma^{1-\alpha}$ when $\alpha$ is fixed as
0.65 and measured PDS coverage in our test dataset.
$\sigma=2\%$ represents that 100MB memory is used per machine for top $k$ PDS.
While the predicted value remains flat, the  real coverage actually increases as the data size
increases, which indicates that $\alpha$ increases with the data size. 
Thus in practice, the coverage of the PDS increases as more VMs are involved.
%Then the deduplication efficiency of PDS approach using top k most popular fingerprints is:
%\begin{equation}
%  e_k = (\frac{m*B}{F*D})^{1-\alpha}
%\end{equation}

% is mainly affected by the its memory usage,
%and the Zipf-like distribution parameter $\alpha$.
%From the memory usage perspective, the more memory we give to PDS index, the more duplicates it can found.
%From the data characteristics perspective, if the system tends to backup arbitrarily random data, 
%$\alpha$ would be small and thus PDS approach would not be effective. But in a VM cluster all VMs
%have a large portion of similar data, thus leading to a bigger $\alpha$. The more VM join the cluster,
%the better deduplication efficiency our PDS deduplication approach will have.

\comments{
Since $B$, $D$ and $F$ are environment constants, the deduplication efficiency of PDS is mainly affected by its memory usage,
and the Zipf-like distribution parameter $\alpha$.
From the memory usage perspective, the more memory we give to PDS index, the more duplicates it can found.
From the data characteristics perspective, if the system tends to backup arbitrarily random data, 
$\alpha$ would be small and thus PDS approach would not be effective. But in a VM cluster all VMs
have a large portion of similar data, thus leading to a bigger $\alpha$. The more VM join the cluster,
the better deduplication efficiency our PDS deduplication approach will have.
}

\comments{ %this table is superceded by the graph below it
\begin{table}
    \begin{tabular}{llll}
    Data size (GB) & 1\%    & 2\%    & 4\%    \\
    14.6           & 18.6\% & 22.1\% & 31.4\% \\
    28.1           & 19.5\% & 26.2\% & 38.8\% \\
    44.2           & 21.7\% & 26.5\% & 36\%   \\
    61.6           & 23.2\% & 32.9\% & 35\%   \\
    74.2           & 23.6\% & 33.6\% & 37.5\% \\
    \end{tabular}
    \caption{Deduplication effectiveness of top k\% of global index}
    \label{tab:cds}
\end{table}
}

@@

%As illustrated in Figure~\ref{??},
%when the number of machines at each cluster increases, the number of total VMs increases.
%Then $k$ increases since more memory is available to host the popular chunks index.
%But for each physical machine, the number of VMs remains the same, and thus
%$D$ is  a constant. Then  the overall deduplication efficiency of VC remains
%p constant.

>>>>

\section{VM-centric Snapshot Deduplication}
\label{sect:dedupe}

\subsection{Key VM-centric  Strategies}
\label{sect:vc-strategies}
\begin{itemize}
\item \textbf{VM-specific local duplicate search within similar segments.}
We start with the standard dirty bit approach in a coarse grain segment level.
In our implementation with Xen at an Alibaba platform, the segment size is 2MB
and  the device driver is extended to support  changed block tracking. 
Since every write for a segment will touch a dirty bit, the device driver maintains dirty bits in memory
and cannot afford a small segment  size.
It should be noted that dirtybit tracking is supported or can be easily implemented in 
major virtualization solution vendors. For example,
the VMWare hypervisor has an API to let external backup applications know 
the changed areas since last backup. 
The Microsoft SDK provides an API that allows external applications to monitor 
the VM's I/O traffic and implement  the changed block tracking feature.

Since the best deduplication uses a nonuniform chunk size 
in the average of 4K or 8K~\cite{??},  
we conduct additional local inner-VM deduplication by comparing
dirty segment's chunk fingerprints within  {\em similar} segments from its parent snapshot. 
We define two segments are similar if their approximated content signature is the same.
This segment signature value is defined as the minimum value of all its chunk fingerprints 
computed during backup and is recorded in the snapshot recipe.
When we are processing a dirty segment,
we can easily find similar segments from the
parent snapshot recipe and load their segment recipes and also set a limit on the 
the number of  similar segments to be  searched. 
 Then 
given a set of data chunks within a dirty segment,  we compare  these chunk fingerprints
with those in similar segments.  
For example, with a 2MB segment, there are about 500 fingerprints to compare. By limiting at most 10 similar
segments to search,
the amount of memory for maintaining those fingerprints in similar segment s is small.

\item \textbf{Cross-VM deduplication with popular chunks and replication support}
This step accomplishes the standard global fingerprint  comparison as conducted
in the previous work~\cite{??}.
One key observation is that the inner deduplication has removed many of the duplicates.
There are fewer deduplication opportunities across VMs while the memory and network
consumption for global comparison is more expensive.
Thus our approximation is that the global fingerprint comparison only searches for the top $k$
most popular items. This dataset is called PDS (common data set). 
The popularity of a chunk is the number  of data chunks  from different VMs
that are duplicates of this chunk after the inner VM deduplication.
This number can be computed periodically on a weekly basis.
Once the popularity of all data chunks is collected, the system only maintains the top $k$
most popular chunk signatures in a distributed shared memory.

Since $k$ is relatively small and these top $k$ chunks are shared among multiple VMs, 
we can afford to provide extra replicas for these popular chunks to enhance the fault resilience.

@@

We have not  adopted the  sampled index~\cite{Guo2011} 
for  popular data chunks and  this is because sampling requires the use of prefetching to be effective.
For the data sets we have tested, the spatial locality is limited among popular
data chunks and  on average the number of consecutive data chunks is 7 among popular chinks, which is not sufficient.

\subsection{Impact on deduplication efficiency}
Choosing the value  $k$ for the most popular chunks affects the deduplication efficiency.
We analyze this impact based on the characteristics  of the VM snapshot traces
studied from  application datasets.
Our previous study shows that the popularity of data chunks after inner VM deduplication follows 
a Zipf-like distribution\cite{zipf} and its
exponent $\alpha$ is ranged between 0.65  and  0.7.~\cite{ieeecloud}. 
Table~\ref{tab:symbol} lists parameters used in this analysis.

@@

@@

We store the popular index using a distributed shared memory hashtable such as MemCacheD
and allocate a fixed percentage of memory space   per physical machine for top $k$ popular items.
As the number of physical machines ($p$) increases,
the entire cloud cluster can host more VMs; however,  ratio $\sigma$ which is $k/c_u$ remains
a constant because each physical machine on average still hosts a fixed constant number of 
VMs. Then the overall deduplication efficiency of VC defined in Formula~\ref{eq:dedupeff}
remains to be a constant.
Thus the deduplication efficiency is stable  as $p$ increases as long as $\sigma$  is a constant.

Ratio $\sigma^{1-\alpha}$ represents the percentage of the remaining
chunks detected as duplicates in global cross-VM deduplication due to PDS.
We call it PDS coverage.
Figure~\ref{fig:cds-coverage} shows predicted PDS coverage using $\sigma^{1-\alpha}$ when $\alpha$ is fixed as
0.65 and measured PDS coverage in our test dataset.
$\sigma=2\%$ represents that 100MB memory is used per machine for top $k$ PDS.
While the predicted value remains flat, the  real coverage actually increases as the data size
increases, which indicates that $\alpha$ increases with the data size. 
Thus in practice, the coverage of the PDS increases as more VMs are involved.

@@

\subsection{Storage Space and Impact on Fault Tolerance}

\begin{figure}
    \centering
    \subfigure[Sharing of data under VM-centric dedup model]
    {
        \includegraphics[width=3in]{images/share_vc}
        \label{fig:share_vc}
    }
    \\
    \subfigure[Sharing of data under VM-oblivious dedup model]
    {
        \includegraphics[width=3in]{images/share_vo}
        \label{fig:share_vo}
    }
    \caption{Bipartite association of VMs and file blocks under VO and VC approaches}
    \label{fig:share}
\end{figure}

The replication degree of the backup storage 
is $r$ for regular file blocks and $r=3$ is a typical setting in the distributed
file system~\cite{Hadoop,GFS}.
In the VC approach, a special replica degree $r_c$ used for PDS blocks where $r_c>r$. 
The storage cost for VO with full deduplication is $c_u *r$ and for VC, it is
$ k*r_c  + (c_u-k)*r$. Thus The storage cost ratio of $VC$ over $VO$ is 
\[
\sigma \frac{r_c}{r} + 1-\sigma
\]
Since $sigma$ is small,  term $\sigma \frac{r_c}{r}$ is small in the above expression.  
Thus the impact on storage increase is very small when we choose a large $\frac{r_c}{r}$ ratio. 
For example, $\frac{r_c}{r}=2$.

Next we  assess  the impact of losing $d$ machines 
to the the VC and VO approaches.  
A large $\frac{r_c}{r}$ ratio can have a positive impact on full availability of snapshot blocks.

We use filesystem blocks rather than a deduplication
data chunk as our unit of failure because the DFS keeps
filesystem blocks as its base unit of storage.
To  compute the full availability of all snapshots of a VM, we derive
the probablity of losing a snapshot file block of a VM by
estimating the number of file system blocks per VM in each approach.
As illustrated in Figure~\ref{fig:share},
we build a bipartite graph representing the association from unique file system blocks
to their corresponding VMs in each approach. An association edge is  drawn  from a file block  to a VM 
if this block is used by this VM. 
For VC, each VM has an 
average number of $N_1$ file system blocks for non-PDS data. 
It also refers  an average of   $N_2$ file system blocks for PDS data. 
For VO, each VM has an average  of  $N_o$ file system blocks
and let $V_o$ be the average number of VMs shared by each file system block.

In VC, each non-PDS file system block is associated with one VM
 and  PDS file system blocks are
shared by an average of $V_c$ VMs. Let $s$ be the average number of chunks per file block. Thus, 
\[
V *p*N_1 *s  = C_u (1-\sigma)\; \mbox{ and } \; 
V *p*N_2 *s  = C_u \sigma *V_c
\]
For the VO approach, 
\[
V *p*N_o *s  = C_u  V_o.
\]

Since each file block (with default size $64MB$) contains many chunks (on average 4KB),
each file block contains the hot low-level chunks shared by many VMs, and it also contains
rare chunks which are not shared.  From the about equations.
\[
\frac{N_1}{N_o}=  \frac{1-\sigma}{V_o}<1.
\] 
Thus when there is a failure in file blocks with replication degree $r$
and there is no failure for PDS data with more replicas,   a VM in
the VC approach has a lower chance to lose a snapshot than the VO approach because
$N_1<N_o$. 
Figure~\ref{fig:fsb-links} shows the number of VMs sharing by each file block.
We can observe that $N_1 +N_2 < N_o$. 
This is likely because the PDS FSBs tightly pack data used by many VMs, 
which decreases the overall number of FSBs required to backup a VM.
If  the backup for multiple VMs is conducted concurrently, there would be more
VMs shared  by each file block on average. Therefore,
even when there is a loss of a PDS block, the VC approach tolerates the fault better.

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
                width=\linewidth,
                height=0.6\linewidth,
		%title={VO FSB links},
		xlabel={Number of VMs},
		ylabel={Avg. Num. VMs sharing FSB},
                cycle list name=mline,
                xmin=0,
                ymin=0,
                xmax=106,
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=north west
		]
                \addplot table[x=VMs,y=FSBLinks] {figures/vo_fsb_links_105.txt};
		\addplot table[x=VMs,y=cdslinks] {figures/cds_links_105.txt};
                \legend{VO, PDS in VC};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of VMs sharing a 64MB FSB with global dedup (VO), and in a 2\% PDS for VC.}
  \label{fig:fsb-links}
\end{figure}

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO VM links},
                width=\linewidth,
                height=0.6\linewidth,
		xlabel={Number of VMs},
		ylabel={Avg. Num. FSBs used by VM},
                xmin=0,
                ymin=0,
                xmax=106,
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=south west
		]
                \addplot[blue,mark=none] table[x=VMs,y=No] {figures/vo_vm_links_105.txt};
                \addplot[red,dotted,mark=none] table[x=VMs,y expr=\thisrow{N1}+\thisrow{N2}] {figures/vc_vm_links_105.txt};
                \addplot[red,dashdotted] table[x=VMs,y=N1] {figures/vc_vm_links_105.txt};
                \addplot[red,densely dashed,mark=none] table[x=VMs,y=N2] {figures/vc_vm_links_105.txt};
                \legend{$N_o$, $N_1+N_2$, $N_1$, $N_2$};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of 64MB FSBs used by a single VM. For VC both the number of PDS and Non-PDS FSBs used are shown.}
  \label{fig:vm-links}
\end{figure}

The full snapshot availability of a VM is estimated as follows with parameters $N_1$, $N_2$, and $N_o$.
With replication degree $r$, the availability of a file block is the probability that  
all of its replicas do not appear in any group of $d$ failed machines. 
Namely, $1-\binom{d}{r}/ \binom{p}{r}$. 
The snapshot availability of a VM  in the VO approach is
\begin{equation}
\label{eq:VO}
(1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_o}. 
\end{equation}

For VC, there are two cases.
\begin{itemize}
\item
When there are $r \le d<r_c$ machines failed,  there is no PDS data loss and  
the full snapshot availability of a VM in the VC approach is 
and is
\[
(1-\frac{\binom{d}{r}} { \binom{p}{r} })^{N_1}.
\]
Since $N_1 <N_o$, the VC approach has a higher availability of VM snapshots than VO.

\item
When $r_c \leq d$, both non-PDS and PDS file blocks in VC can have a loss.
The full snapshot availability of  a VM in the VC approach is
\[
(1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_1} 
*
(1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} })^{N_2}.
\]
Figure~\ref{fig:fsb-availability} illustrates that the availability of an individual file system block
with different replication degree. This demonstrates inequality $1-\frac{ \binom{d}{r}} { \binom{p}{r} }
< 1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} }$. As we have also observed
$N_1+N_2 <N_o$ in our dataset, these two conditions support that VC has a  higher availability. 
%comparing  Formula~\ref{eq:VO} and~\ref{eq:VC}. 
\end{itemize}

\begin{figure}[htbp]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
                width=\linewidth,
                height=0.6\linewidth,
            %title={FSB Availability},
            cycle list name=mline,
            xlabel={Number of Machines Failed},
            ylabel={Availability of Single FSB (\%)},
            extra y ticks={99.9}, %to add extra ticks
            mark options=solid,
            legend pos=south west,
            %legend columns=2,
            %legend style={
            %    at={(0.5,-0.2)},
            %anchor=north}
            ]
            \addplot table[x=NodesFailed,y=Availability5] {figures/fsb_availability.txt};
            \addplot table[x=NodesFailed,y=Availability4] {figures/fsb_availability.txt};
            \addplot table[x=NodesFailed,y=Availability3] {figures/fsb_availability.txt};
            \legend{$R=5$,$R=4$,$R=3$};
            \end{axis}
    \end{tikzpicture}
    \caption{Availability of individual file system blocks in a 100 machine cluster with different replication degrees.}
  \label{fig:fsb-availability}
\end{figure}
